### 2021-07-10 docs/manuscript/manuscript.tex
improve methods: sigm

The input function is a sigmoid function described by Eq~\ref{ec:input-func}.
\begin{equation}
 g(u^i) = \frac{1}{1 + \exp(a - b \cdot u^i)},
 \label{ec:input-func}
\end{equation}
\noindent
in which $a$ is the sigmoid steepness, equal to 5; $a/b$ is the threshold value,
set to 1 for all simulations, and $u^i$ is the following equation:
\begin{equation}
 u^i = \sum_j w_{ij} \cdot [G]^j_n + w_{im} \cdot [M]_n.
 \label{ec:mat-sum}
\end{equation}

>>>>

The input function is a sigmoid function described by Eq~\ref{ec:input-func}.
Sigmoid functions are often used to approximate Hill functions describing gene
activation/inhibition, and this approach has been used extensively to model the
response of signaling pathways and gene interactions in GRNs \cite{mendoza2006,
vu2007, zhang2013, armao2016}. Moreover, differential equation models using
sigmoid functions have shown to fit gene expression data \cite{chen2005,
dahlquist2015}.

\begin{equation}
 g(u^i) = \frac{1}{1 + \exp(a - b \cdot u^i)},
 \label{ec:input-func}
\end{equation}
\noindent
in which $a$ is the sigmoid steepness, equal to 5; $a/b$ is the threshold value,
set to 1 for all simulations, and $u^i$ is the following equation:
\begin{equation}
 u^i = \sum_j w_{ij} \cdot [G]^j_n + w_{im} \cdot [M]_n.
 \label{ec:mat-sum}
\end{equation}
